---
title: "p8105_hw1_cyl2159"
author: "Chhiring Lama"
date: "2024-09-17"
output:
  html_document:
    toc: true
    toc_float: true

---

```{r setup, include=FALSE}
library(tidyverse)
```

## *Problem 1*

Importing penguin dataset:
```{r import_data, message=FALSE}
data("penguins", package = "palmerpenguins")
```

```{r calculate_mean, echo = FALSE}
mean_flipper <- mean(pull(penguins, flipper_length_mm),na.rm = TRUE)
```

The dataset `penguins` is a data frame consisting of information regarding species, their residing islands, sex, their bill's length and depth, flipper's length, body-mass index, sex and the year the data was collected. These data are provided by the individual variables ``r (names(penguins)[-length(names(penguins))])`` and ``r (names(penguins)[length(names(penguins))])``respectively. There are `r (nrow(penguins))` rows/observations and `r (ncol(penguins))` columns. The mean flipper length for penguins is `r round(mean_flipper, digits =2)` mm. 

Making a scatterplot of flipper_length_mm (y) vs bill_length_mm (x):
```{r scatter_plot, warning = FALSE}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("scatter_plot_flipper_length_vs_bill_length.pdf", height = 4, width = 6)
```

## *Problem 2*

Creating a dataframe with 10 observations with a random sample variable from a normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector and a factor vector with 3 levels: 
```{r create_df}
example_df <- tibble(
  sample_var = rnorm(10), 
  log_var = sample_var > 0, 
  char_var = c("a", "b", "c", "d", "b", "a", "c", "d", "f", "g"), 
  factor_var = factor(c("NY", "NJ", "NY", "MA", "MA", "MA", "NY", "NY", "NJ", "NJ"))
)

```

Trying to calculate and outputting mean for each variable:
```{r mean_calc}
mean(pull(example_df, sample_var))
mean(pull(example_df, log_var))
mean(pull(example_df, char_var))
mean(pull(example_df, factor_var))
```

Here, we are able to calculate mean for `sample_var` and `log_var`, but cannot do so for `char_var` and `factor_var` as they are not numeric or binary variables. 

If we coerce them to be a numeric value as shown below:
```{r mean_calc_after_coercing, eval = FALSE}
mean(pull(example_df, as.numeric(sample_var)))
mean(pull(example_df, as.numeric(log_var)))
mean(pull(example_df, as.numeric(char_var)))
mean(pull(example_df, as.numeric(factor_var)))
```

This will also calculate the mean for `char_var` and `factor_var` as NA. However, because we are forcing variable to be numeric and the inherently character values in these two variables cannot be converted to a numeric type, they will all be considered missing values (NAs). As a result, the mean for these variable with be NA, and we will get a warning message. 






